Fluent statistical computing interfaces for biological data analysis

### 2020-07-15 Rmd/04-intron.Rmd
add intro para

>>>>

In the study of gene regulation, there is much interest in uncovering the
effects of aberrant minor class splicing (called U12 splicing) on the transcriptome.
Minor class splicing is a regulatory process where a class of 
introns (called U12 introns in this case but there exist other classes in eukaryotic organisms) are removed from pre-mRNA prior to gene expression. The removal of these introns is catalysed by small ribonucleoproteins (snRNPs)
which identify key motifs and branch sites in the intron to begin splicing.
Here we describe an exploratory workflow for finding coverage traces
with evidence for intron retention using a knockout experiment in zebrafish.
